A weighted sampling algorithm for the design of RNA sequences with targeted secondary structure and nucleotides distribution

### 2013-04-11 ISMB/supplementary_ISMB.tex
typos corrected

\subsection{Benchmark other softwares}
To evaluate the performances of \ourprog, we benchmark a set of classical softwares lacking \GCContent control. Those are \RNAinverse, \INFORNA, \NUPACK and \frankenstein. We present in Fig.~\ref{fig:no_gc_control} the average sequence identity and frequency
for sequences generated them.

\begin{figure*}[ht!]
  \centering
  \includegraphics[width=\textwidth]{Figures/entropy_nogc}
  \caption{The average sequence identity and frequency for softwares without \GCContent control.}
  \label{fig:no_gc_control}
\end{figure*}

@@

\begin{figure*}[ht!]
  \centering
  \includegraphics[width=\textwidth]{Figures/struct_solved_vsrnainverse.png}
  \caption{The first row shows the number of structures for which one generated sequence has the 
  structure as MFE when only using \ourprog. The second row shows when we process \ourprog results with \RNAinverse.}
  \label{fig:nb_sols}
\end{figure*}

>>>>

\subsection{Benchmark other softwares}
To evaluate the performances of \ourprog, we benchmark a set of classical softwares lacking \GCContent control. Those are \RNAinverse, \INFORNA, \NUPACK and \frankenstein. We present in Fig.~\ref{fig:no_gc_control} the average sequence identity and frequency
for the sequences that generated them.

\begin{figure*}[ht!]
  \centering
  \includegraphics[width=\textwidth]{Figures/entropy_nogc.pdf}
  \caption{The average sequence identity and frequency for softwares without \GCContent control.}
  \label{fig:no_gc_control}
\end{figure*}

@@

\begin{figure*}[ht!]
  \centering
  \includegraphics[width=\textwidth]{Figures/struct_solved_vsrnainverse.pdf}
  \caption{The first row shows the number of structures for which one generated sequence has the 
  structure as MFE when only using \ourprog. The second row shows when we process \ourprog results with \RNAinverse.}
  \label{fig:nb_sols}
\end{figure*}
